\tool

### 2018-04-17 paper/paper.tex
Updates to implementation walkthrough and approach

\documentclass[sigconf,review,anonymous]{acmart}
\acmConference[ESEC/FSE 2018]{The 26th ACM Joint European Software Engineering Conference and Symposium on the Foundations of Software Engineering}{4–9 November, 2018}{Lake Buena Vista, Florida, United States}
\usepackage{pdftexcmds}
%\usepackage[pdftex]{graphicx}
%\usepackage{multirow}
%\usepackage{pgfplots}
\usepackage{tikz}
\usepackage{balance}
\usepackage{amssymb, marvosym}
\usepackage{threeparttable}
%\usepackage[bookmarks=false]{hyperref}
\usepackage{url}
\PassOptionsToPackage{hyphens}{url}
\hypersetup{colorlinks=true,breaklinks=true}
\usetikzlibrary{patterns,shapes,arrows}
\newcommand\tab[1][.5cm]{\hspace*{#1}}
\hyphenation{op-tical net-works semi-conduc-tor}
\raggedbottom
\newcommand{\tool}{\textsl{tool-recommender-bot}}

@@

@@

@@

Brown and colleages defined demonstrating a desire to adopt a particular behavior as users expressing interest in ``discovering, using, or learning more information'' about a new practice. In software engineering, developers desire to write high-quality programs without errors. This desire is demonstrated by the fact software engineers spend the majority their time testing and debugging programs~\cite{NIST}. Our approach capitalizes on developers' desires to produce mistake-free code by commending developers for their work. Futhermore, psychology research shows that people respond better to praise than blame~\cite{PraiseAndBlame}. To help improve tool adoption among software engineers, our approach analyzes code changes made by developers to determine their intentions, then compliments the developer on their attempt to improve the code quality.

%\tool~aims to increase tool discovery by recommending software engineering tools designed to promote developers' desires for improving software quality.

%Our goal is for \tool~to increase awareness of software engineering tools. For our initial evaluation in this paper, we  recommending \textsc{Error Prone}. \textsc{Error Prone} is a static analysis tool that uses a suite of defined bug patterns to detect errors in Java code. Static analysis tools like \textsc{Error Prone} are useful for debugging and preventing errors in source code for applications, however they are often underutilized by software engineers~\cite{Johnson2013Why}.

@@

Familiarity is also a key part of receptiveness and important in increasing adoption of a target behavior. Fogg suggests users are more likely to adopt a target behavior if they are familiar with it~\cite{FoggPersuasive}. To improve usage of software engineering tools, our approach integrates familiarity. First, we make recommendations based on developers' contributions to recent projects. Scalabrino and colleagues claim code understandability is one of the most important factors for software development, maintenance, debugging, and testing~\cite{Scalabrino2017Understandability}. Developers should be familiar with the project before making changes to the code base. More specifically, our approach apprehends similar pieces of code the developer may also want to change. After analyzing the code changes and commending the developer on their work, our approach analyzes the entire code base to search for similar opportunities for improvement.

%To choose a familiar audience, our approach makes recommendations on proposed Github code changes submitted by users. Developers should be knowledgeable and familiar with the changes they propose, as well as the code base to which they are contributing. \tool~suggests \textsc{Error Prone} when a reported error is fixed by a developer in a pull request or commit, and the same bug exists elsewhere in the code.

@@

After integrating user receptiveness into our design, the final step is to make a recommendation.

To implement our approach, we developed \tool~to recommend \textsc{Error Prone} to GitHub developers. This section gives an overview describing the general process of how the automated recommendation system works.

@@

This sections provides technical details on the implementation of our approach in \tool. The design of our system is motivated by current practices in the software engineering industry to make \tool~similar to a peer for developers.

@@

\subsection{Code Reviews}

Code reviews between developers are a standard procedure of software engineering teams to improve code quality~\cite{CodeReviewingTrenches}. This practice also applies to GitHub projects, with many repositories requiring approval from another developer before changes can be merged into the main code base~\cite{PullRequestReview}. Our approach simulates peer code reviews by making recommendations for static analysis tools as a comment on pull requests and commits. Github allows users to make comments on specific lines of code in situ with the code changes. \tool~determines where to automatically make recommendation comments by converting the line number of the identified fix to the equivalent position in the diff file, or textual representation of code changes made in a commit or pull request, represented by the number of lines below the ``@@'' symbol in the header\footnote{https://developer.github.com/v3/pulls/comments/\#create-a-comment}.

@@

To evaluate the effectiveness of our approach, we compared \tool~to different styles and mediums of tool recommendations

@@

To analyze 700+ GitHub repositories simultaneously, we used Ansible\footnote{https://www.ansible.com/} to generate Jenkins jobs running \tool~on multiple virtual machines.

To answer our first research question, we observed how often our approach makes recommendations on commits and pull requests. In addition to the frequency of recommendations, we also tracked instances where \textsc{Error Prone} defects were removed but not reported as fixed according to our fix identification algorithm in Section III.B.2, the number of occurrences where errors were fixed but no other instances of that bug were found in the code, and the false positive rate.

@@

@@

@@

@@

To improve discovery of software engineering tools, we plan to increase the practicality of \tool~for researchers to implement our system with their projects. A next step is to extend our approach to work with multiple static analysis tools, such as Checkstyle\footnote{http://checkstyle.sourceforge.net/} for Java. This will allow us to have more opportunities to make recommendations to developers based on the output from different tools. Additionally, we plan to update our system to work with software engineering tools that integrate as plugins for different build systems such as Gradle\footnote{https://gradle.org/} and Travis CI\footnote{https://travis-ci.org/}, as opposed to just Maven projects. Future work will also extend \tool~to work with different types of tools to increase adoption and usage, for example Find Security Bugs\footnote{https://find-sec-bugs.github.io/} which is useful for finding security vulnerabilities in Java web applications. Finally, future work will consist of expanding \tool~to work with software engineering tools for different programming languages, such as the Pylint\footnote{https://www.pylint.org/} static analysis tool for Python, clang\footnote{https://clang.llvm.org/} compiler and static analyzer for C and C++, and more.

>>>>

\documentclass[sigconf,review,anonymous]{acmart}
\acmConference[ESEC/FSE 2018]{The 26th ACM Joint European Software Engineering Conference and Symposium on the Foundations of Software Engineering}{4–9 November, 2018}{Lake Buena Vista, Florida, United States}
\usepackage{pdftexcmds}
%\usepackage[pdftex]{graphicx}
\usepackage{multirow}
\usepackage{pgfplots}
\usepackage{tikz}
\usepackage{balance}
\usepackage{amssymb, marvosym}
\usepackage{threeparttable}
%\usepackage[bookmarks=false]{hyperref}
\usepackage{url}
\PassOptionsToPackage{hyphens}{url}
\hypersetup{colorlinks=true,breaklinks=true}
\usetikzlibrary{patterns,shapes,arrows}
\newcommand\tab[1][.5cm]{\hspace*{#1}}
\hyphenation{op-tical net-works semi-conduc-tor}
\raggedbottom
\newcommand{\tool}{\textsl{tool-recommender-bot}}

@@

The first design principle of our approach finds places where a tool would be useful. To do this, our technique commends developers for their updates making improvements to code. We analyze code changes made by developers and then praise them for their work when they improve the quality of code. Additionally, psychology research also suggests people respond better to praise than blame~\cite{PraiseAndBlame}. Our approach applauds developers when they produce good work rather than rebuke them for making mistakes when they introduce new issues.

To determine improvements in code quality, our approach monitors problems reported by the output of software engineering tools. For example, suppose we want to use our approach to increase awareness of useful refactoring tools. To do this, our technique will inspect code changes made by developers to determine if a refactoring activity occurs. If a refactoring activity is detected, then we commend the programmer for their work to improve the quality of the code.

%Our goal is for \tool~to increase awareness of software engineering tools. For our initial evaluation in this paper, we  recommending \textsc{Error Prone}.

Next, our approach finds additional places to recommend useful software engineering tools. To find other opportunities for recommendations, we apprehend instances where developers can make source code improvements similar to their previous code changes and based on development tool analysis from the commend phase. This design principle helps reduce effort and provides information-related needs to software engineers, which Fischer suggests is a goal for help systems~\cite{Fischer1984ActiveHelpSystems}.

After commending software engineers for their work, our approach automatically finds opportunities to make similar changes to improve the code. For example, after the programmer completes the refactoring task, we analyze the entire updated version of the code base to find other places where the same refactoring activity is applicable.

%To choose a familiar audience, our approach makes recommendations on proposed Github code changes submitted by users.

The final step of our approach is to recommend useful software engineering tools to developers. The recommendation to developers includes commending them for improving code quality and apprehending new opportunities for similar improvements. In our example, the recommendation to the developer will praise them for their work refactoring the code, provide additional places in the code where they can make similar refactoring changes, and then suggest the refactoring tool which is useful for detecting even more instances for refactoring activities. Our goal is that through commending and apprehending, we can improve the effectiveness of recommendations for software engineering tools and increase adoption among developers.

%TODO: Non-lossy image
%TODO: More interesting error
\begin{figure*}
	\includegraphics[width=\textwidth]{images/screenshot.png}
	\caption{Screenshot of recommendation from \tool}	
	\label{fig:tool} 
\end{figure*}

@@

\subsubsection{Demonstrate Desire}

Brown and colleages defined demonstrating a desire to adopt a particular behavior as users expressing interest in ``discovering, using, or learning more information'' about a new practice. In software engineering, developers desire to write high-quality programs without errors. This desire is demonstrated by the fact software engineers spend the majority their time testing and debugging programs~\cite{NIST}. Our approach capitalizes on developers' desires to produce mistake-free code by commending developers for their work. To help improve tool adoption among software engineers, our approach analyzes code changes made by developers to determine their intentions, then compliments the developer on their attempt to improve the code quality.

\subsubsection{Familiarity}

Familiarity is also a key part of receptiveness and important in increasing adoption of a target behavior. Fogg suggests users are more likely to adopt a target behavior if they are familiar with it~\cite{FoggPersuasive}. To improve usage of software engineering tools, our approach integrates familiarity. First, we make recommendations based on developers' contributions to recent projects. Scalabrino and colleagues claim code understandability is one of the most important factors for software development, maintenance, debugging, and testing~\cite{Scalabrino2017Understandability}. Developers should be familiar with the project before making changes to the code base. More specifically, our approach apprehends code the developer may also want to change based on their previous update.

To implement our approach, we developed \tool~to recommend the \textsc{Error Prone} static analysis tool to developers on GitHub. This section provides a general overview of how our automated recommendation system works.

@@

First, a GitHub user makes a change to a repository. \tool~automatically analyzes to commits and pull requests GitHub projects to find opportunities to commend developers when bugs reported by \textsc{Error Prone} are removed. \textsc{Error Prone} is a static analysis tool that uses a suite of defined bug patterns to detect errors in Java code. Static analysis tools like \textsc{Error Prone} are useful for debugging and preventing errors in source code for applications, however they are often underutilized by software engineers~\cite{Johnson2013Why}. More details on how our implementation determines a bug fix can be found in Section 6.2.

@@

Next, \tool~apprehends places where similar opportunities to the code can be made. GitHub should be knowledgeable and familiar with the changes they propose, as well as the code base to which they are contributing. \tool~suggests \textsc{Error Prone} when a reported bug is fixed by a developer in a commit or pull request, but the same error still exists elsewhere in the code.

@@

Finally, \tool~recommends \textsc{Error Prone} to the GitHub user at the location of their fix in the code. We commend developers by telling them ``Good job!'' and presenting the error they fixed. \tool~ provides the apprehended opportunities for similar code changes as links to buggy lines with the same error in other parts of the code. Finally, we provide a link to the \textsc{Error Prone} website for users to learn more about the tool if they are interested. Figure \ref{fig:tool} provides a sample recommendation from \tool~to a developer for \textsc{Error Prone} on a GitHub pull request.

@@

This sections provides technical details on the implementation of our approach in \tool. The design of our system is motivated by current practices in the software engineering industry to make \tool~more similar to a peer for developers.

@@

\subsection{Code Review}

Code reviews between developers are a standard procedure of software engineering teams to improve code quality~\cite{CodeReviewingTrenches}. This practice also applies to GitHub projects, with many repositories requiring approval from another developer before changes can be merged into the main code base~\cite{PullRequestReview}. Our approach simulates peer code reviews by making recommendations for static analysis tools as a comment on pull requests and commits. Github allows users to make comments on specific lines of code in situ with the code changes. \tool~determines where to automatically make recommendation comments by converting the line number of the identified fix to the equivalent position in the diff file, or textual representation of code changes made in a commit or pull request, represented by the number of lines below the ``@@'' symbol in the header\footnote{https://developer.github.com/v3/pulls/comments/\#create-a-comment}. An example of a comment from \tool~is displayed in Figure \ref{fig:tool}.

@@

To evaluate the effectiveness of our approach, we compared \tool~to different styles and mediums of tool recommendations.

@@

To analyze 700+ GitHub repositories simultaneously, we set up \tool~on virtual machines. We used Ansible\footnote{https://www.ansible.com/} to automatically generate and provision Jenkins jobs for every project. To limit the load on each machine, we ran our study in parallel by dividing the Jenkins jobs among \textit{n} virtual CentOS images. The scripts and instructions to used setup our study environment for \tool~are publicly available to view online.

To test the effectiveness of our approach, we used four different recommendation styles based on our design principles of commending developers for their work and apprehending opportunities to make similar changes. The four recommendation styles include commending and apprehending, commending only, apprehending only, and neither commending nor apprehending. In each case, a recommendation was always made. We adapted \tool~to make recommendations without commending or without apprehending. %TODO: Without commendation,...
Without apprehending, our system simply commends the developer for their fix and does not link to similar errors found in other parts of the code. For the final recommendation without commending or apprehending, we decided to send recommendations to developers by email without commending them for their patch and not providing other instances to make a similar fix. An overview of each style is presented in Table~\ref{table:styles}.

\begin{table*}
\begin{center}
\caption{Study Recommendation Styles}
\begin{tabular*}{\textwidth}{ c|c|p{5cm}|p{5cm}| }
  \multicolumn{2}{ c }{\textbf{}} & \multicolumn{2}{ c }{\textbf{Commend}} \\ \cline{2-4}
 & & Yes & No \\ \cline{2-4}
\multirow{2}{*}{\textbf{Apprehend}} 
	 & Yes & \tool  & Modified \tool~(without commending) \\ \cline{2-4}
	 & No & Modified \tool~(without apprehending) &  Email  \\ \cline{2-4}
\end{tabular*}
\label{table:styles}
\end{center}
\end{table*}

\subsubsection{Recommendation Review}

@@

\subsubsection{Debriefing}

@@

To determine the effectiveness of our approach, we observed how often\tool~makes recommendations on commits and pull requests. In addition to the frequency of recommendations, we also tracked instances where \textsc{Error Prone} defects were removed but not reported as fixed according to our fix identification algorithm in Section III.B.2, the number of occurrences where errors were fixed but no other instances of that bug were found in the code, and the false positive rate.

@@

\subsubsection{Recommend}

\subsubsection{Commend, Recommend}

\subsubsection{Apprehend, Recommend}

\subsubsection{Commend, Apprehend, Recommend}

@@

The main goal of our future work is to increase the practicality of \tool~for researchers and toolsmiths to implement our approach with their tools. A next step is to implement our approach with multiple static analysis tools, such as Checkstyle\footnote{http://checkstyle.sourceforge.net/} for Java. This will allow us to have more opportunities to make recommendations to developers based on the output from different tools. Additionally, we plan to update our system to work with software engineering tools that integrate as plugins for different build systems such as Gradle\footnote{https://gradle.org/} and Travis CI\footnote{https://travis-ci.org/}, as opposed to just Maven projects. Future work will also extend \tool~to work with different types of tools to increase adoption and usage, for example Find Security Bugs\footnote{https://find-sec-bugs.github.io/} which is useful for finding security vulnerabilities in Java web applications. Finally, future work will consist of expanding \tool~to work with software engineering tools for different programming languages, such as the Pylint\footnote{https://www.pylint.org/} static analysis tool for Python, clang\footnote{https://clang.llvm.org/} compiler and static analyzer for C and C++, and more.
